---
title: "315-group-project"
author: "Jackson Meehan, Jacob Coffey, Esha Gupta, Stotra Pandya"
date: '2023-05-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 
```{r}
library(readr)
merged_airbnb <- read_csv("~/Documents/36315/merged_airbnb.csv", show_col_types = FALSE)
```

```{r}
library(tidyverse)

cheaper_airbnbs = subset(merged_airbnb, realSum < quantile(merged_airbnb$realSum, probs = .9))

cheaper_airbnbs %>%
  ggplot(aes(x = dist, y = realSum)) +
  facet_wrap(city ~ .) + 
  geom_point(alpha = 0.3) +
  geom_smooth(method="loess", se=TRUE) +
  labs(title="Distance From Center City vs. Price of Airbnb in Different European Cities",
       x = "Distance From Center City", y="Price of Airbnb Listing")
```

# research questions

## RQ1

How does the relationship between different variables and price and the relationship between different variables and guest satisfaction differ between cities in Europe?

## RQ2

On what characteristics do the Airbnb's differ across European cities?

## RQ3

What is the association between whether or not it is a weekend and the price for Airbnb's in European cities?


